Modal Abstractions for Virtualizing Memory Addresses

### 2023-04-05 programlogic.tex
+

\subsubsection{Register To Memory}
 \paragraph{Register To Physical Memory} First one is to

\paragraph{Register To Virtual Memory}
\subsubsection{Register To Register}
\paragraph{Updating \lstinline|cr3|}

>>>>

\subsubsection{Register To Memory}\todo[inline,color=red]{Iso:explain}
 \paragraph{Register To Physical Memory}\todo[inline,color=red]{Iso:explain}
\paragraph{Register To Virtual Memory} \todo[inline,color=red]{Iso:explain}
\subsubsection{Register To Register}\todo[inline,color=red]{Iso:explain}
\paragraph{Updating \lstinline|cr3|}\todo[inline,color=red]{Iso:explain}

### 2023-04-05 soundness.tex
+

We prefer to skip explaining the steps used in instantiation of Iris because it is an almost standard procedure, has already been explained for many other logic \ref{}, and we are concerned with the page-count limitation. However, it is worh noting that once you instantiate Iris for your language, it comes with the semantic definition for the weakest-precondition which we can refactor into Hoare triples, $\triple\pre\instr\post$, to specify our  selected \textsf{AMD64} instructions, and show that these triples are sound.

\subsection{The Soundness Statement}
\label{def:soundness:statement}
The operational semantics of our simple lang just executes sequences of instructions in our x86-64 model. Therefore, our soundness argument is to show that any execution composed of instructions in our machine model (some of which are shown in Figure \sref{sec:semantics}) does not end-up in a invalid state. In other words, a~program that attempts to ... stuck~(\sref{sec:instrsemantics}).
\begin{theorem}[Soundness of the Logic]
  \label{th:adequacy}
 Together with the assumptions on the initial state hold,
 the execution of the instruction~$\instrs$, beginning with this initial state, cannot result in a configuration where the execution is stuck.
\end{theorem}
which states that if the program~$\instr$, with the given \textsf{valid\_init} asserting a valid state initialization, satisfies a semantic Hoare
triple, then this program cannot crash: by a direct consequence of Iris's adequacy theorem~\cite[\S6.4]{iris}.
\todo{ismail, give the real adeq. theorem here}
Moreover we need to show the validity of each rules in Figures \fref{fig:reasoning} and \fref{fig:laws}.
\begin{theorem}[Validity of the Reasoning Rules]
\label{th:validity}
  Each of the rules in Figures~\ref{fig:laws}
  and~\ref{fig:reasoning} is valid.
\end{theorem}
Due to the space limits in this paper, we do not mention each proof for these rules explicitly (which are already mechanized in Coq),
but the definitions and constructions used requires explanation.

Together, Theorems~\ref{th:adequacy} and~\ref{th:validity} guarantee that, if
the Hoare triple $\textsf{valid\_init }\instrs\;\iTrue$ can be obtained by applying
the reasoning rules of our logic, then the program~$\instrs$ is safe.
\subsection{BI-Lifting for Address Space Modality}
\label{sec:bilifting}

>>>>

We prefer to skip explaining the steps used in instantiation of Iris because it is an almost standard procedure, has already been explained for many other logic \ref{}, and we are concerned with the page-count limitation. However, it is worh noting that once you instantiate Iris for your language, it comes with the semantic definition for the weakest-precondition which we can refactor into Hoare triples, $\triple\pre\instr\post$, to specify our  selected \textsf{AMD64} instructions shown in Figure \ref{fig:wpdamd}, and show that these triples are sound. 
\subsection{The Soundness Statement}
\label{def:soundness:statement}
The operational semantics of our simple lang just executes sequences of instructions in our x86-64 model. Therefore, our soundness argument is to show that any execution composed of instructions in our machine model (some of which are shown in Figure \sref{sec:semantics}) does not end-up in a invalid state.
\begin{figure*}
\small
\begin{mathpar}
\inferrule[Skip]{}{
  \triple\post\iskip\post
}

\inferrule[Seq]{
  \triple\pre{\instr_1}\midpoint \\
  \triple\midpoint{\instr_2}\post
}{
  \triple\pre{(\iseq{\instr_1}{\instr_2})}\post
}
\end{mathpar}
\caption{Structural Rules for Executing Instructions}
\Description{Reasoning Rules}
\label{fig:structural}
\end{figure*}

\begin{theorem}[Soundness of the Logic]
  \label{th:adequacy}
 Together with the assumptions on the initial state hold,
 the execution of the instruction~$\instrs$, beginning with this initial state, cannot result in a configuration where the execution is stuck.
\end{theorem}
which states that if the program~$\instr$, with the given \textsf{valid\_init} asserting a valid state initialization, satisfies a semantic Hoare
triple, then this program cannot crash: by a direct consequence of Iris's adequacy theorem~\cite[\S6.4]{iris}.

Moreover we need to show the validity of each rules in Figures \fref{fig:reasoning} and \fref{fig:laws}.
\begin{theorem}[Validity of the Reasoning Rules]
\label{th:validity}
  Each of the rules in Figures~\ref{fig:wpdamd}
  and~\ref{fig:structural} is valid.
\end{theorem}
Due to the space limits in this paper, we do not mention each proof for these rules explicitly (which are already mechanized in Coq),
but the definitions and constructions used requires explanation.

Together, Theorems~\ref{th:adequacy} and~\ref{th:validity} guarantee that, if
the Hoare triple $\textsf{valid\_init }\instrs\;\iTrue$ can be obtained by applying
the reasoning rules of our logic, then the program~$\instrs$ is safe.
